Assessment of zonal symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2020-11-25 analysis/paper2/paper2.Rmd
Funciona localmente

bibliography: 
  - AsymSAM.bib
  - packages.bib
bibstyle: spphys
# bibstyle options spbasic(default), spphys, spmpsci
output: 
  bookdown::pdf_book: 
      base_format: rticles::springer_article
      latex_engine: "xelatex"
      # citation_package: "natbib"
header-includes: 
 - \usepackage{gensymb}
 - \usepackage{subfig}
 - \usepackage[inline]{showlabels}
 - \usepackage{chngcntr}
 - \usepackage{natbib}
---

>>>>

bibliography: 
  - AsymSAM
  - packages
bibstyle: spphys
# bibstyle options spbasic(default), spphys, spmpsci
output: 
  bookdown::pdf_book: 
      base_format: rticles::springer_article
      latex_engine: "xelatex"
      # citation_package: "natbib"
header-includes: 
 - \usepackage{gensymb}
 - \usepackage{subfig}
 - \usepackage[inline]{showlabels}
 - \usepackage{chngcntr}
 - \usepackage{natbib}
---
